Reproducible Research in R: A Tutorial on how to Do the Same Thing More Than Once

### 2021-11-23 manuscript.Rmd
align headin levels
force build for examples even when up to date

```{r, echo=FALSE, results='asis'}
cat("```bash",
  stringi::stri_wrap(system2("make", " --dry-run data/simulation_results.csv", stdout = TRUE)),
  "```", sep = "\n")
```

@@

```{r, echo=FALSE, results='asis'}
cat("```bash",
  stringi::stri_wrap(system2("make", " --dry-run DOCKER=TRUE simulated_data.csv", stdout = TRUE)),
  "```", sep = "\n")
```

@@

### Alternatives to simulated data

@@

#### When Is PAC Applicable?

@@

We ahve argued that PAC has several advantages over classic preregistration and have outlined its implementation.
To illustrate how PAC works in practice and help researchers to implement PAC themselves, we provide a worked example.
We will use an exemplary research question that was based on openly available data:

>>>>

```{r, echo=FALSE, results='asis'}
cat("```bash",
  stringi::stri_wrap(system2("make", "-B --dry-run data/simulation_results.csv", stdout = TRUE)),
  "```", sep = "\n")
```

@@

```{r, echo=FALSE, results='asis'}
cat("```bash",
  stringi::stri_wrap(system2("make", "-B --dry-run DOCKER=TRUE simulated_data.csv", stdout = TRUE)),
  "```", sep = "\n")
```

@@

## Alternatives to simulated data

@@

## When Is PAC Applicable?

@@

We have argued that PAC has several advantages over classic preregistration and have outlined its implementation.
To illustrate how PAC works in practice and help researchers to implement PAC themselves, we provide a worked example.
We will use an exemplary research question that was based on openly available data:
